One-stage point transect distance sampling using iterated integrated nested Laplace approximations

### 2024-10-26 paper.tex
bibtex edits

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{caption}
\usepackage{textcomp}    % for Hawaii characters

@@

\author[Andrew E. Seaton {\it et al.}]{Andrew E. Seaton}
\address{School of Mathematics \& Statistics, 
	University of Glasgow, 
	Glasgow,
	UK}
\email{andrew.seaton.2@glasgow.ac.uk}

@@

The SPDE approach can at first appear to be fundamentally different  other approaches such as penalised regression splines.  However, the two methods are closely related and the GRF model component in our model plays a similar role to a penalised smoothing spline on space.  \cite{yue_bayesian_2014} show how spline models can be viewed through the perspective of SPDEs and \cite{ miller_understanding_2019} do the reverse to show how to implement the Mat\'ern SPDE as a penalised spline model in \texttt{mgcv} \citep{wood_gam_2017}.

>>>>

\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{caption}
\usepackage{textcomp}    % for Hawaii characters
\usepackage{url}

@@

\author[Andrew E. Seaton {\it et al.}]{Andrew E. Seaton}
\address{School of Biodiversity, One Health and Veterinary Medicine, 
	University of Glasgow, 
	Glasgow,
	UK}
\email{andrew.seaton.2@glasgow.ac.uk}

@@

The SPDE approach can at first appear to be fundamentally different  other approaches such as penalised regression splines.  However, the two methods are closely related and the GRF model component in our model plays a similar role to a penalised smoothing spline on space.  \cite{yue_bayesian_2014} show how spline models can be viewed through the perspective of SPDEs and \cite{miller_UnderstandingStochasticPartial_2020} do the reverse to show how to implement the Mat\'ern SPDE as a penalised spline model in \texttt{mgcv} \citep{wood_gam_2017}.
